Quality Assesment of OpenStreetMap Footpath Data for 3D City Modelling

### 2020-05-09 report/report.tex
Table indents
Update table references

\begin{table}[H]
\begin{tabular}{lllll}
                  & Footpath & Residential & Secondary & Primary \\
    Minimum width & 2.0 m    & 6.0 m       & 6.5 m     & 8.0 m   \\
    Maximum width & 5.0 m    & 9.0 m       & 10.0 m    & 16.0 m
\end{tabular}
\end{table}

@@

\begin{table}[H]
\begin{tabular}{lllll}
    & Total number of buildings & Area cover \\
    OSM & 102755 & 33105023.32... $m^2$ \\
    SLU & 170783 & 33718628.97... $m^2$
\end{tabular}
\end{table}

\begin{table}[H]
\begin{tabular}{lllll}
    & Number of buildings (\%) & Area cover (\%) \\
    OSM & 60.17\% & 98.18\% \\
    SLU & 100.00\% & 100.00\%
\end{tabular}
\end{table}

@@

\begin{table}[H]
\begin{tabular}{lllll}
    $e_{average}$ & $e_{max}$ & $e_{min}$ & $e_{standard deviation}$ \\
    2.0579... & 9.9878... & 0.0 & 1.2464...
\end{tabular}
\end{table}

@@

\begin{table}[H]
\begin{tabular}{lllll}
    & 1:0 & 1:1 & 1:n & Total \\
    Match count & 9812   & 81722   & 11221   & 102755 \\
    Percent     & 9.55\% & 79.53\% & 10.92\% & 100\%
\end{tabular}
\end{table}

@@

\end{tabular}
\end{table}

@@

\end{tabular}
\end{table}

>>>>

\begin{table}[H]
    \begin{tabular}{lllll}
                      & Footpath & Residential & Secondary & Primary \\
        Minimum width & 2.0 m    & 6.0 m       & 6.5 m     & 8.0 m   \\
        Maximum width & 5.0 m    & 9.0 m       & 10.0 m    & 16.0 m
    \end{tabular}
    \captionof{table}{Standard road widths used for the collision study}
    \label{table:road-widths}
\end{table}

@@

\begin{table}[H]
    \begin{tabular}{lllll}
        & Total number of buildings & Area cover \\
        OSM & 102755 & 33105023.32... $m^2$ \\
        SLU & 170783 & 33718628.97... $m^2$
    \end{tabular}
    \captionof{table}{Total number of buildings and their cumulative area}
    \label{table:num-of-buildings}
\end{table}

\begin{table}[H]
    \begin{tabular}{lllll}
        & Number of buildings (\%) & Area cover (\%) \\
        OSM & 60.17\% & 98.18\% \\
        SLU & 100.00\% & 100.00\%
    \end{tabular}
    \captionof{table}{Total number of buildings and cumulative area as percentages}
    \label{table:num-of-buildings-percent}
\end{table}

@@

\begin{table}[H]
    \begin{tabular}{lllll}
        $e_{average}$ & $e_{max}$ & $e_{min}$ & $e_{standard deviation}$ \\
        2.0579... & 9.9878... & 0.0 & 1.2464...
    \end{tabular}
    \captionof{table}{The estimated positional accuracy of the OSM dataset: average, max, min and standard deviation}
    \label{table:positional-accuracy}
\end{table}

@@

\begin{table}[H]
    \begin{tabular}{lllll}
        & 1:0 & 1:1 & 1:n & Total \\
        Match count & 9812   & 81722   & 11221   & 102755 \\
        Percent     & 9.55\% & 79.53\% & 10.92\% & 100\%
    \end{tabular}
    \captionof{table}{The number and percentages of matching buildings between both datasets, ordered by type of correlation (1:0, 1:1 or 1:n)}
    \label{table:building-matching}
\end{table}

@@

    \end{tabular}
    \captionof{table}{The first result table of the collision study. This table shows the amount of features and edges, as well as the cumulative edge length, in total and which are intersecting with any other feature.}
    \label{table:road-collision}
\end{table}

@@

    \end{tabular}
    \captionof{table}{The second result table of the collision study. This table shows the amount of features and edges, as well as the cumulative edge length, which can be corrected by simple geometric translation.}
    \label{table:road-collision-corrected}
\end{table}
